A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
AST size percentages

To roughly estimate the complexity of the code being evaluated,
Fig.~\ref{fig:ast-size} shows the distribution of the abstract syntax tree
size of the \c{expr} argument to \eval. The majority of inputs across core
and packages (\miss{XX}\%) is 1. That is to say, the code being evaluated
consists of a single variable name or constant. A function call needs at
least three nodes. Inputs smaller than \c{X} nodes account for 95\% of all
calls. Sizes are roughly similar between core and packages.

>>>>

To roughly estimate the complexity of the code being evaluated,
Fig.~\ref{fig:ast-size} shows the distribution of the abstract syntax tree
size of the \c{expr} argument to \eval. The majority of inputs across core
and packages (\NbAstOnePercent of \eval calls and \NbAstOneCallSitePercent of call sites) is 1. That is to say, the code being evaluated
consists of a single variable name or constant. A function call needs at
least three nodes. Inputs smaller than \AstSizeNineFive nodes account for 95\% of all
calls. Sizes are roughly similar between core and packages.
